Future cosmic microwave background delensing with galaxy surveys.

### 2017-10-05 Notes/galaxy_delensing.tex
remove intensity mapping

Finally, we consider the Square Kilometre Array (SKA).
The SKA is a planned radio array that will survey large scale structure primarily by detecting the redshifted neutral hydrogen (HI) 21cm emission line from a large number of galaxies out to high redshift. 
We will assume an intensity mapping survey mode where SKA will measure the large-scale fluctuations of the \textit{integrated} 21cm intensity from many unresolved galaxies.  
We model both the redshift distribution and  bias of radio sources following \cite{namikawa:2016a}. 
In \reffig{kernel}, we compare the CMB lensing kernel $W^{\kappa}(z)$ to the kernels $W^{g}(z)$ of all the tracers introduced here.

@@

Furthermore, we are not considering the uncertainties on galaxy survey internal parameters such as biases, source distributions and photometric redshift uncertainties. These uncertaintes can significantly degrade inflationary constraints \cite{sherwin:2015,namikawa:2016a}.
However, as shown in \cite{sherwin:2015,namikawa:2016a}, these can be auto-calibrated i.e. they can be tightly constrained using galaxy survey auto- and cross-correlation spectra. We checked this for a few of the tracer combinations used here and find it particularly true once several tracers are jointly taken into account.
Finally, although we have assumed a Gaussian covariance $\sigma( C_{\ell}^{BB} )$ it actually has small non-Gaussian contributions \cite{motloch:2017,benoit-levy:2012}. This approximation is good enough to show the improvement due to delensing.
The approximations made here go in the direction of a slightly optimistic \textit{absolute} value for the parameters statistical uncertainties both for the standard and the delensed case. The delensing improvement is defined as the \textit{relative} value of these uncertainties $\alpha_{i} = \sigma^{\rm{del}}(i)/\sigma(i)$ and, at first order, it is not affected by this assumptions.

>>>>

Finally, we consider the Square Kilometre Array (SKA).
The SKA is a planned radio array that will survey large scale structure primarily by detecting the redshifted neutral hydrogen (HI) 21cm emission line from a large number of galaxies out to high redshift. 
We will assume a radio continuum survey mode where SKA will detect radio galaxies through their total emission out to very high redshift.  
We model both the redshift distribution and  bias of radio sources following \cite{namikawa:2016a}. 
In \reffig{kernel}, we compare the CMB lensing kernel $W^{\kappa}(z)$ to the kernels $W^{g}(z)$ of all the tracers introduced here.

@@

Furthermore, we are not considering the uncertainties on galaxy survey internal parameters such as biases, source distributions and photometric redshift uncertainties. These uncertaintes can significantly degrade inflationary constraints \cite{sherwin:2015,namikawa:2016a}.
However, as shown in \cite{sherwin:2015,namikawa:2016a}, these can be auto-calibrated i.e. they can be tightly constrained using galaxy survey auto- and cross-correlation spectra. We checked this for a few of the tracer combinations used here and find it particularly true once several tracers are jointly taken into account.
Finally, although we have assumed a Gaussian covariance $\sigma( C_{\ell}^{BB} )$ it actually has a non-Gaussian contribution \cite{motloch:2017,benoit-levy:2012}. This approximation is good enough to show the improvement due to delensing.
The approximations made here go in the direction of a slightly optimistic \textit{absolute} value for the parameters statistical uncertainties both for the standard and the delensed case. The delensing improvement is defined as the \textit{relative} value of these uncertainties $\alpha_{i} = \sigma^{\rm{del}}(i)/\sigma(i)$ and, at first order, it is not affected by this assumptions.
